---
title: "estimate_R"
author: "Hongsheng Xie"
date: "3/28/2022"
# updated by Hongsheng Xie 5/1/2022
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(EpiEstim)
library(dplyr)
library(ggplot2)
library(epitrix)
```

# Calculate the parameters of delayed gamma distribution from infection to death.
```{r}
gamma_mucv2shapescale(mu = 23.9, cv = 0.4)
# mean = 23.9, sd = 9.56, α = 6.25, β = 3.824
```

# Data processing
```{r}
series.data <- read.csv("C:/Users/danie/Desktop/CMU/Statistical Practice/deaths_teaching_mobility_posture.csv")

# Correct death data with value less than 0
series.data$rev_newdeaths <- as.integer(round(ifelse(series.data$rev_newdeaths<0, 0, series.data$rev_newdeaths),digits=0))

# Correct confirmed data with value less than 0
series.data$rev_newconfirmed2 <- as.integer(round(ifelse(series.data$rev_newconfirmed2<0, 0, series.data$rev_newconfirmed2), digits=0))

# Select the interval start at 2020.6.1
series.data.R <- series.data[11267:33599+27,]
```

# Calculate estimate R_t from death and case for top 9 popular counties in Ohio
```{r, warning = FALSE, message = FALSE}
new_data = data.frame(county=character(), window=numeric(), date=character(), R.deaths=numeric(), R.deaths10=numeric(), R.cases=numeric())
county = c("BUTLER","CUYAHOGA","FRANKLIN","HAMILTON","LAKE","LORAIN","LUCAS","MONTGOMERY","STARK","SUMMIT")

# Go through counties
for (c in county) {
  # Select the date, deaths, and cases columns from the dataset
  c.data <- dplyr::filter(series.data.R, county==c)[,c(2,12,14)]
  
  # death_scaled equals to 10 times of deaths. It is used to check if a simple change in scale will affect the estimation of Rt.
  c.data$death_scaled <- (c.data$rev_newdeaths)*10
  
  # estimate Rt for each county using time series of deaths
  config.d = make_config(incid = c.data$rev_newdeaths, 
                         t_start = c(2:(nrow(c.data)-6)),
                         t_end = c(8:(nrow(c.data))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  R.d <- estimate_R(incid=c.data$rev_newdeaths, 
                    method="non_parametric_si", 
                    config=config.d)
  # estimate Rt for each county using time series of scaled deaths
  config.d_sc = make_config(incid = c.data$death_scaled, 
                         t_start = c(2:(nrow(c.data)-6)),
                         t_end = c(8:(nrow(c.data))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  
  R.d_sc <- estimate_R(incid=c.data$death_scaled, 
                       method="non_parametric_si", 
                       config=config.d_sc)
  
  # estimate Rt for each county using time series of cases
  config.c = make_config(incid = c.data$rev_newconfirmed2, 
                          t_start = c(2:(nrow(c.data)-6)),
                          t_end = c(8:(nrow(c.data))),
                          method="non_parametric_si", 
                          si_distr = dgamma(0:100,shape = (1/0.6)^2, 
                                            scale = (15.2*(0.6^2))))
  
  R.c <- estimate_R(incid=c.data$rev_newconfirmed2, 
                     method="non_parametric_si", 
                     config=config.c)
  
  # aggregate Rt from death, scaled death, and case with their 95% condifance interval to a dataset
  counties.R <- data.frame(county = rep(c,times=length(R.d$R$`Mean(R)`)),
                           date = c.data$date[8:length(c.data$date)], 
                           R.deaths = R.d$R$`Mean(R)`,
                           R.deaths10 = R.d_sc$R$`Mean(R)`,
                           R.deaths.q2.5 = R.d$R$`Quantile.0.025(R)`, 
                           R.deaths.q97.5 = R.d$R$`Quantile.0.975(R)`,
                           R.cases = R.c$R$`Mean(R)`,
                           R.cases.q2.5 = R.c$R$`Quantile.0.025(R)`, 
                           R.cases.q97.5 = R.c$R$`Quantile.0.975(R)`
                           )
    
  new_data <- rbind(new_data, counties.R)
}  
```

# Create a time series object
```{r}
library(hrbrthemes)
new_data <- merge(series.data.R, new_data, by=c("county","date")) 

new_data$date <- as.Date(new_data$date)
```

# Plot time series of Rt.
```{r}
c = "BUTLER"
d <- dplyr::filter(new_data, county==c)

# Plot Rt from death and case in Bulter
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "CUYAHOGA"
d <- dplyr::filter(new_data, county==c)

# Plot Rt from death and case in Cuyahoga
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "HAMILTON"
d <- dplyr::filter(new_data, county==c)

# Plot Rt from death and case in Hamilton
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "SUMMIT"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Summit
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "MONTGOMERY"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Montgomery
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "LUCAS"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Lucas
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "STARK"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Stark
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "LORAIN"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Lorain
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))

c = "LAKE"
d <- dplyr::filter(new_data, county==c)
# Plot Rt from death and case in Lake
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",c,"with window equal to 7 days"))
```

# Calculate estimate Rt from death and case in counties with different postures
```{r, warning = FALSE, message = FALSE}
new_data2 = data.frame(county=character(), window=numeric(), date=character(), R.deaths=numeric(), R.deaths10=numeric(),R.case2=numeric())

teach_post = unique(series.data$major_teaching)

# Go through 3 different teaching postures
for (t in teach_post) {
  t.data <- filter(series.data.R, major_teaching==t)[,c(2,12,14)]
  
  # aggregate the number of death on date
  teach_post_d <- t.data %>%
    group_by(date) %>% 
    summarise(teach_death = sum(rev_newdeaths))
  teach_post_d$death_scaled <- (teach_post_d$teach_death)*10
  
  # aggregate the number of case on date
  teach_post_c <- t.data %>%
    group_by(date) %>% 
    summarise(teach_case = sum(rev_newconfirmed2))

  # estimate Rt for each teaching posture using time series of deaths
  config.d = make_config(incid = teach_post_d$teach_death, 
                         t_start = c(2:(nrow(c.data)-6)),
                         t_end = c(8:(nrow(c.data))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  R.d <- estimate_R(incid=teach_post_d$teach_death, 
                    method="non_parametric_si", 
                    config=config.d)

  # estimate Rt for each teaching posture using time series of scaled deaths
  config.d_sc = make_config(incid = teach_post_d$death_scaled, 
                         t_start = c(2:(nrow(c.data)-6)),
                         t_end = c(8:(nrow(c.data))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  R.d_sc <- estimate_R(incid=teach_post_d$death_scaled, 
                       method="non_parametric_si", 
                       config=config.d_sc)
  
  # estimate Rt for each teaching posture using time series of cases
  config.c = make_config(incid = teach_post_c$teach_case, 
                          t_start = c(2:(nrow(c.data)-6)),
                          t_end = c(8:(nrow(c.data))),
                          method="non_parametric_si", 
                          si_distr = dgamma(0:100,shape = (1/0.6)^2, 
                                            scale = (15.2*(0.6^2))))
  
  R.c <- estimate_R(incid=teach_post_c$teach_case, 
                     method="non_parametric_si", 
                     config=config.c)
  
  # aggregate Rt from death, scaled death, and case with their 95% condifance interval to a dataset
  teach_post.R <- data.frame(posture = rep(t,times=length(R.d$R$`Mean(R)`)),
                           date = teach_post_d$date[8:length(teach_post_d$date)], 
                           R.deaths = R.d$R$`Mean(R)`,
                           R.deaths10 = R.d_sc$R$`Mean(R)`,
                           R.deaths.q2.5 = R.d$R$`Quantile.0.025(R)`, 
                           R.deaths.q97.5 = R.d$R$`Quantile.0.975(R)`,
                           R.cases = R.c$R$`Mean(R)`,
                           R.cases.q2.5 = R.c$R$`Quantile.0.025(R)`, 
                           R.cases.q97.5 = R.c$R$`Quantile.0.975(R)`
                           )
    
  new_data2 <- rbind(new_data2, teach_post.R)
}
```

```{r}
new_data2$date <- as.Date(new_data2$date)
```

```{r}
p = "Hybrid"
d <- dplyr::filter(new_data2, posture==p)
# Plot Rt from death and case for Hybrid teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",p,"with window equal to 7 days"))

p = "On Premises"
d <- dplyr::filter(new_data2, posture==p)
# Plot Rt from death and case for On Premises teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",p,"with window equal to 7 days"))

p = "Online Only"
d <- dplyr::filter(new_data2, posture==p)
# Plot Rt from death and case for Online Only teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of",p,"with window equal to 7 days"))

# Plot Rt from death for three different teaching posture
ggplot(data = new_data2,aes(x=date,y=R.deaths,group = posture,
                           colour=as.factor(posture))) + 
  geom_line() + 
  ggtitle("Rt time series from death for three different teaching posture with window equal to 7 days")

# Plot Rt from case for three different teaching posture
ggplot(data = new_data2,aes(x=date,y=R.cases,group = posture,
                           colour=as.factor(posture))) + 
  geom_line() + 
  ggtitle("Rt time series from case for three different teaching posture with window equal to 7 days")
```

# Calculate estimate Rt of the top 3 popular counties for each teaching posture
```{r}
new_data3 = data.frame(county=character(), window=numeric(), date=character(), R.deaths=numeric(), R.deaths10=numeric(),R.cases=numeric())
teach_post <- unique(series.data.R$major_teaching_end)

# Go through the major teaching posture
for (t in teach_post) {
  
  # Select all data with a specific teaching posture
  t.data <- dplyr::filter(series.data.R,major_teaching_end==t)[,c(2,3,7,12,14,39)]
  
  # Get all counties with that teaching posture as majority
  county_post <- unique(t.data$county)
  max1 = 0
  max2 = 0
  max3 = 0
  big1 = ""
  big2 = ""
  big3 = ""
  
  # Go through all teaching posture
  for (c in county_post) {
    c.data <- filter(t.data, county==c)
    
    # Population of this county is larger than that of currenlt third popular county
    if (c.data$population[1] > max3) {
      max3 <- c.data$population[1]
      big3 <- c
    }
    
    # This county is more popular than the most popular county
    if (max3 > max1) {
      tmp_p <- max3
      tmp_c <- big3
      max3 <- max2
      big3 <- big2
      max2 <- max1
      big2 <- big1
      max1 <- tmp_p
      big1 <- tmp_c
    # This county less popular than the most popular county but more popular than the 2nd popular county
    } else if (max3 > max2) {
      tmp_p <- max3
      tmp_c <- big3
      max3 <- max2
      big3 <- big2
      max2 <- tmp_p
      big2 <- tmp_c
    }
  }
  
  # Select the data for the top 3 counties
  t_popCounty <- filter(t.data, county==big1 
                        | county==big2
                        | county==big3)
  
  # Aggregate the number of deaths for each day
  teach_post_d <- t_popCounty %>%
    group_by(date) %>% 
    summarise(teach_death = sum(rev_newdeaths))
  
  # Aggregate the number of cases for each day
  teach_post_c <- t_popCounty %>%
    group_by(date) %>% 
    summarise(teach_case = sum(rev_newconfirmed2))
  
  # estimate Rt for each teaching posture using time series of deaths
  config.d = make_config(incid = teach_post_d$teach_death, 
                         t_start = c(2:(nrow(teach_post_d)-6)),
                         t_end = c(8:(nrow(teach_post_d))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  R.d <- estimate_R(incid=teach_post_d$teach_death, 
                    method="non_parametric_si", 
                    config=config.d)
  
  # estimate Rt for each teaching posture using time series of scaled deaths
  teach_post_d$death_scaled <- (teach_post_d$teach_death)*10

  config.d_sc = make_config(incid = teach_post_d$death_scaled, 
                         t_start = c(2:(nrow(teach_post_d)-6)),
                         t_end = c(8:(nrow(teach_post_d))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 6.25, scale = 3.824))
  
  R.d_sc <- estimate_R(incid=teach_post_d$death_scaled, 
                       method="non_parametric_si", 
                       config=config.d_sc)
  
  # estimate Rt for each teaching posture using time series of cases
  config.case2 = make_config(incid = teach_post_c$teach_case, 
                         t_start = c(2:(nrow(teach_post_c)-6)),
                         t_end = c(8:(nrow(teach_post_c))),
                         method="non_parametric_si", 
                         si_distr = dgamma(0:100,shape = 2.78, scale = 3.672))
  
  R.case2 <- estimate_R(incid=teach_post_c$teach_case, 
                       method="non_parametric_si", 
                       config=config.case2)
  
  # combine Rt from death, scaled death, and case with their 95% condifance intervals to a dataset
  teach_post.R <- data.frame(teach_post = rep(t,times=length(R.d$R$`Mean(R)`)),
                             date=teach_post_d$date[8:length(teach_post_d$date)],
                             R.deaths = R.d$R$`Mean(R)`,
                             R.deaths10 = R.d_sc$R$`Mean(R)`,
                             R.deaths.q2.5 = R.d$R$`Quantile.0.025(R)`, 
                             R.deaths.q97.5 = R.d$R$`Quantile.0.975(R)`,
                             R.cases = R.case2$R$`Mean(R)`,
                             R.cases.q2.5 = R.case2$R$`Quantile.0.025(R)`, 
                             R.cases.q97.5 = R.case2$R$`Quantile.0.975(R)`)
    
  new_data3 <- rbind(new_data3, teach_post.R)
}  
```

```{r}
new_data3$date <- as.Date(new_data3$date)

p <- "Hybrid"
d <- dplyr::filter(new_data3, teach_post==p)

# Plot Rt from death and case for top 3 popular On Premises teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of top 3 counties with posture ",p," with window 7"))

p <- "On_Premises"
d <- dplyr::filter(new_data3, teach_post==p)
# Plot Rt from death and case for top 3 popular On Premises teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of top 3 counties with posture ",p," with window 7"))

p <- "Online_Only"
d <- dplyr::filter(new_data3, teach_post==p)
# Plot Rt from death and case for top 3 popular Online Only teaching posture
ggplot(d, aes(x=date,y=R.deaths)) + 
  theme_classic()+
  geom_rect(aes(xmin = as.Date("2020-08-15"),xmax = as.Date("2020-12-15"),ymin=-Inf,ymax=Inf),alpha=0.1,colour="grey",fill="grey")+
  geom_line(aes(y = R.deaths), color = "red") + 
  geom_line(aes(y = R.cases), color="blue") +
  geom_ribbon(aes(ymin=R.deaths.q2.5,ymax=R.deaths.q97.5), fill="#FF9999", alpha=0.5) +
  geom_ribbon(aes(ymin=R.cases.q2.5,ymax=R.cases.q97.5), fill="#99FFFF", alpha=0.5) +
  ylim(0,10)+
  
  labs(
      x="Date",
      y="R_t") +
  ggtitle(paste("Estimate Rt from death(red) and case(blue) of top 3 counties with posture ",p," with window 7"))

# Plot Rt from death for top 3 popular for each major teaching posture
ggplot(data = new_data3,aes(x=date,y=R.deaths,group = teach_post,
                           colour=as.factor(teach_post))) + 
  geom_line() + 
  labs(
      x="Date",
      y="R_t") +
  ggtitle("Rt from death for top 3 counties in each posture with 7 days as window")

# Plot Rt from scaled death for top 3 popular for each major teaching posture
ggplot(data = new_data3,aes(x=date,y=R.deaths10,group = teach_post,
                           colour=as.factor(teach_post))) + 
  geom_line() + 
  labs(
      x="Date",
      y="R_t") +
  ggtitle("Rt from scaled death for top 3 counties in each posture with 7 days as window")

# Plot Rt from case for top 3 popular for each major teaching posture
ggplot(data = new_data3,aes(x=date,y=R.cases,group = teach_post,
                           colour=as.factor(teach_post))) + 
  geom_line() +
  labs(
      x="Date",
      y="R_t") +
  ggtitle("Rt from case for top 3 counties in each posture with 7 days as window")
```


